### 2014-03-12 src/methodology.Rnw
update

\subsubsection{x\% selection over program elements}
Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
extended x\% selection to sample from within different program elements.
We sampled in the increasing order of scope, --- \textit{line},
\textit{method} and \textit{class} (\textit{project} scope was
analyzed as part of x\% selection).

While the criteria is simple, it is not immediately clear when we
are faced with program elements that produced too few mutants for a particular
fraction to yield at-least one mutant. For example, for a line that produced
15 mutants, the number of mutants that can be chosen in \textit{(x\%, line,
1/64)} is less than 1. We analyzed the results of the following criterias:
1) to apply \textit{round} function to the resulting number and covert to
the nearest integer, and choose that value as the number of mutants (in
effect, ignoring elements that are less complex), 2) to apply \textit{ceil}
function to the resulting value, ensuring that there is atleast one mutant
per program element, and 3) to apply \textit{sample} criteria suggested by
Zhang et al.~\cite{zhang2013ase}, which chooses a mutant with given fracton
as probability.
% TODO: If the criterias ceil and round does not make sense, we might remove them to gain space.

\subsubsection{Lines per element}
Our previous research~\cite{gopinath2014code} found that statement coverage was highly correlated with mutation coverage for a project. This immediately suggests that perhaps choosing one mutant per line may be sufficient to achieve a close approximation of the final mutation score. Further, statement deletion has been researched previously~\cite{untch2009onreduced,deng2013empirical} and has been found to reduce the number of mutants well, without an appreciable decrease in accuracy. This also provides a nice comparison with similar number of mutants between operator selection and random sampling of mutants.

A simple extension of this approach is to extend this strategy as previously, by choosing as many number of mutants as there are number of lines in a program element, and we can extend it as before to sample \textit{1/2,1/4,1/8,1/16,1/32,1/64} of the mutants thus chosen. We chose the rounding strategy for fractional samples for simplicity.
% TODO: Actually do the other rounding choices.

Here too, we have a few choices when sampling mutants. We could either choose the fraction of mutants within the program element, or we could apply the sampling externally. For example, using $\lambda_E$ as number of lines in an element, for \textit{(lpe, $1/2$, method)}, we first get $1/2 \times \lambda_{Method}$ number of mutants from each method. The second alternative is to get $\lambda_{Method}$ number of mutants for all methods, then from this larger set, choose only half of the mutants.

\subsubsection{One per element}
An extremely simple strategy of sampling is to just choose one mutant per program element, which as before, we extended to include all the fractions \textit{1/2,1/4,1/8,1/16,1/32,1/64}.

\subsection{Operator Selection}
% TODO expand as required

>>>>

\subsubsection{x\% selection over program elements (and variations)}
Following the suggestion of Zhang et al.~\cite{zhang2013ase}, we
extended x\% selection criteria to sample from within different program
elements.  We sampled in the increasing order of scope,
--- \textit{line}, \textit{method} and \textit{class} (\textit{project}
scope was analyzed as part of x\% selection).

When the number of mutants to be chosen was not a whole number, we used
the formula suggested by Zhang et a.~\cite{zhang2013ase}, and used the
decimal part to select a mutant with that probability.

Next, we modified this criteria slightly, and instead of choosing a mutant
with probability of decimal part, applied \texit{round(sample)} to round
it to the nearest whole number. We used this as the number of samples to
be chosen from the population. Our aim was to remove elements that was
too simple. That is, if the number of mutants dropped below a threshold
determined by the mutant reduction ratio, that program element did not
contribute any thing to the final result.

Next, we explored in the other direction, by forcing the program elements
to return atleast one element by using the \textit{ceil(sample)}. That is,
irrespective of the fraction being sampled, the simplest elements always
contributed atleast one mutant to the total sample.

\subsubsection{Lines per element and variants}
Our previous research~\cite{gopinath2014code} found that statement coverage
was highly correlated with mutation coverage for a project. This immediately
suggests that perhaps choosing one mutant per line may be sufficient to achieve
a close approximation of the final mutation score. Further, statement deletion
has been researched previously~\cite{untch2009onreduced,deng2013empirical} and
has been found to reduce the number of mutants well, without an appreciable
decrease in accuracy. This also provides a nice comparison with similar
number of mutants between operator selection and random sampling of mutants.

We next extended it to sample from each method instead, but using the number
of lines in the method as the number of mutants to be sampled. This provided
a test of hypothesis of how important the coverage was. This was extended
to class and project scope also.

\subsubsection{One per element}
Another simple strategy of sampling we experimented with is to just choose
one mutant per program element, in the order \textit{line},\textit{method},
\textit{class}.

\subsection{Operator Selection}
